Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-08-18 bbbq_article.tex
No empty headers in supmat, thanks @fransbianchi

@@

@@

@@

>>>>

See Supplementary Figure \ref{fig:snp_rel_pos}
for the distribution of the relative position of the SNPs.

@@

See supplementary Table \ref{tab:tmh_binders_mhc2} 
for the percentage of MHC-II 14-mers overlapping with TMH.

@@

See supplementary Table \ref{tab:elution} 
for the percentages of epitopes derived from a TMH 
found in the two elution studies, 
for the two different kind of topology prediction tools.

@@

See supplementary Table \ref{tab:tmh_binders_mhc1} 
for the percentage of MHC-I 9-mers overlapping with TMH.
